LAGOS lake depth

### 2020-05-11 figures/01_geometry.Rmd
list more package dependencies, remove jsta package dependence

# jsta::jheatmap(dt)
# jsta::jheatmap(dt, "inlake_slope.y")
jsta::jheatmap(
  dplyr::select(dt, 
                slope_online_mean,
                inlake_slope_mean,
                slope_mean, 
                slope_mean_ne,
                dist_deepest, 
                dist_viscenter, 
                maxdepth,
                meandepth))

>>>>

# jsta::jheatmap
jheatmap(
  dplyr::select(dt, 
                slope_online_mean,
                inlake_slope_mean,
                slope_mean, 
                slope_mean_ne,
                dist_deepest, 
                dist_viscenter, 
                maxdepth,
                meandepth))
